\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Virt}
LASS (Laboratory fo Advanced Software Systems)\\
  \url{http://lass.cs.umass.edu/~shenoy/courses/spring11/lectures/Lec05.pdf}

\bibitem{VPS_IBM}
Softlayer, an IBM Company.\\
  \url{http://www.softlayer.com/info/vps}\\
  \url{https://www.softlayer.com/Store/orderComputingInstance/1640,1644,2202}

\bibitem{VPS_Gigas}
Gigas, the cloud hosting company.\\
  \url{https://gigas.com/cloud-vps}

\bibitem{VPS_Axarnet}
Axarnet, VPS no administrado.\\
  \url{https://www.axarnet.es/servidores-vps/servidor-virtual-privado-no-administrado/}

\bibitem{VPS_Axarnet_admin}
Axarnet, VPS administrados.\\
  \url{https://www.axarnet.es/servidores-vps/windows-linux-server-administrado/}

\bibitem{VPS_Axarnet_admin_2}
Axarnet, VPS administrados(sólo linux).\\
  \url{https://www.axarnet.es/servidores-vps/linux-server-administrado/}

\bibitem{VMSW}
Virtual Machine. Wikipedia, the free encyclopedia.\\
  \url{https://en.wikipedia.org/wiki/Virtual_machine}

\bibitem{Adeos}
Adaptive Domain Environment for perating Systems. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Adaptive_Domain_Environment_for_Operating_Systems}

\bibitem{QEMU}
QEMU. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/QEMU}

\bibitem{DOSEMU}
DOSEMU. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/DOSEMU}

\bibitem{DOSBox}
DOSBox. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/DOSBox}

\bibitem{KVM}
Kernel-based Virtual Machine. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Kernel-based_Virtual_Machine}

\bibitem{Hoja_Datos}
Windows Server 2012 R2 Datasheet, June 14, proporcionado por
\href{http://www.microsoft.com/es-es/server-cloud/products/windows-server-2012-r2/}{esta página}

\bibitem{Overview}
Windows Server 2012 R2 Overview, proporcionado por
\href{http://www.microsoft.com/es-es/server-cloud/products/windows-server-2012-r2/}{esta página}

\bibitem{TechWeek}
TechWeek, revista bisemanal de tecnología.\\
  \url{http://www.techweek.es/servidores/noticias/1011002005001/windows-server-2012-funciones-cloud-privado-publico-hyper-v.1.html}

\bibitem{Ubuntu}
Ubuntu. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Ubuntu_(operating_system)}

\bibitem{Canonical}
Canonical. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Canonical_(company)}

\bibitem{MAAS}
MAAS, Metal As A Service, the official website.\\
  \url{http://maas.ubuntu.com/docs1.5/}

\bibitem{Fedora}
Fedora. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Fedora_(operating_system)}

\bibitem{CentOS}
CentOS. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/CentOS}

\bibitem{RedHat}
Red Hat Enterprise Linux. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Red_Hat_Enterprise_Linux}

\bibitem{cita}
Max Spevack, diciembre, 2006.\\
  Fedora Project Leader Max Spevack Responds\\

\bibitem{Market_Share_global}
W3Techs, Web Technology Surveys.\\
  \url{http://w3techs.com/technologies/overview/operating_system/all}

\bibitem{Market_Share_yearly}
W3Techs, Web Technology Surveys.\\
  \url{http://w3techs.com/technologies/history_overview/operating_system/ms/y}

\bibitem{Market_Share_unix}
W3Techs, Web Technology Surveys.\\
  \url{http://w3techs.com/technologies/details/os-unix/all/all}

\bibitem{Market_Share_linux}
W3Techs, Web Technology Surveys.\\
  \url{http://w3techs.com/technologies/details/os-linux/all/all}

\bibitem{HWvsSW}
Hardware RAID vs. Software RAID: Which Implementation is Best for my Application?\\
  \url{http://www.adaptec.com/nr/rdonlyres/14b2fd84-f7a0-4ac5-a07a-214123ea3dd6/0/4423_sw_hwraid_10.pdf}

\bibitem{RAID_RedHat}
Red Hat Enterprise Linux 3: Manual de administración del sistema.\\
  Capítulo 3. 3.3. Hardware y Software RAID.\\
  \url{http://web.mit.edu/rhel-doc/3/rhel-sag-es-3/s1-raid-approaches.html}

\bibitem{LVM}
Logical Volume Manager. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Logical_Volume_Manager_(Linux)}

\bibitem{Var}
The Linux Documentation Project.\\
  \url{http://www.tldp.org/LDP/Linux-Filesystem-Hierarchy/html/var.html}

\bibitem{swap}
Disk Encryption. Archlinux Wiki.\\
  \url{https://wiki.archlinux.org/index.php/Disk_encryption}

\bibitem{boot}
Encrypting an entire system. Archlinux Wiki.\\
  \url{https://wiki.archlinux.org/index.php/Dm-crypt/Encrypting_an_entire_system}

\bibitem{ext2}
Ext2. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Ext2}

\bibitem{ext3}
Ext3. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Ext3}

\bibitem{ext4}
Ext4. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Ext4}

\bibitem{btrfs}
Btrfs. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Btrfs}

\bibitem{JFS}
JFS. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/JFS_(file_system)}

\bibitem{XFS}
XFS. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/XFS}

\bibitem{FAT}
FAT. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/File_Allocation_Table}

\bibitem{NTFS}
NTFS. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/NTFS}

\bibitem{journaling}
Journaling file system. Wikipedia, the free encyclopedia.\\
  \url{http://en.wikipedia.org/wiki/Journaling_file_system}

\bibitem{man_grub-install}
Ubuntu manuals\\
grub-install(8) - Linux man page\\
  \url{http://manpages.ubuntu.com/manpages/trusty/en/man8/grub-install.8.html}

\bibitem{man_dd}
Ubuntu manuals\\
dd(1) - Linux man page\\
\url{http://manpages.ubuntu.com/manpages/karmic/en/man1/dd.1.html}

\bibitem{W12_v}
INTERNET YA, Soluciones Web.\\
Windows Server 2012 – Ediciones Datacenter y Standard.\\
  \url{http://www.internetya.co/windows-server-2012-ediciones-datacenter-y-standard/}

\bibitem{man_bash}
GNU Operating System\\
Bash Reference Manual\\
\url{http://www.gnu.org/software/bash/manual/bash.html}

\bibitem{GNURL}
GNU Operating System\\
The GNU Readline Library\\
\url{http://www.gnu.org/s/readline/}

\bibitem{man_man}
Ubuntu manuals\\
man(1) - Linux man page\\
\url{http://manpages.ubuntu.com/manpages/precise/en/man1/man.1.html}

\bibitem{man_less}
Ubuntu manuals\\
less(1) - Linux man page\\
\url{http://manpages.ubuntu.com/manpages/hardy/man1/less.1.html}

\end{thebibliography}

